Measuring Individual Partisan Harm in Redistricting

### 2021-10-14 paper/paper.Rmd
Update paper.Rmd
abstract

---
title: Measuring Individual Partisan Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: |
      To whom correspondence should be addressed. 
      The authors thank ____ for helpful comments and discussion.
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - individual standing
bibliography: references.bib
biblio-style: apalike
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
---

@@

\begin{proof}
\end{proof}
```
<!--
# Computing Utility, Harm, and Fairness from Precinct-level Election Data {#app:formulas}

@@

Formulas here.
-->
# Districting Measures in New Jersey {#app:nj}

>>>>

---
title: Measuring Individual Partisan Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: |
      To whom correspondence should be addressed. 
      The authors thank {you} for helpful comments and discussion.
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Standards for assessing gerrymandering have often focused on the symmetric treatment of parties by electoral systems. By focusing on counterfactual redistricting plans, we develop measures of utility in district-based representation. We use this to introduce an alternative quantity of interest, partisan fairness, and measures of deviations from this, differential harm. We offer strategies for estimating these measures by leveraging advances in redistricting sampling methodologies which can allow for generating large numbers of legal and feasible plans from a specified target distribution which encapsulates the stated legal constraints for a districting plan. We apply our measures to an example in New Jersey and demonstrate how the basis in counterfactual districting plans allows for straightforward interpretation.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - individual standing
bibliography: references.bib
biblio-style: apalike
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options: 
  markdown: 
    wrap: sentence
---

@@

\begin{proof}
\end{proof}
```
```{=html}
<!--
# Computing Utility, Harm, and Fairness from Precinct-level Election Data {#app:formulas}

@@

Formulas here.
-->
```
# Districting Measures in New Jersey {#app:nj}
